\abstract{

Feature selection is considered a critical stage in classifying omics data. Our goal here is to identify and select the small number of highly critical features that increase the accuracy and decrease the cost for data classification. We have seen that with TCGA multi-omics data that has high dimensionality, the small set of features lead to over-fitting of the classification models. Thus there is an urgent need for a method that can adequately select the most important features.
A commonly used feature selection scheme uses an autoencoder to select the most significant features and thus improve the classification performance. The standard variant of the autoencoder however does not perform well in the attempt to provide original features. In this paper, we introduce a novel global feature selection method that is based on concrete relaxation discrete random variable selection. This uses a specialized concrete feature section layer acting as an encoder along with the standard autoencoder design. A standard neural network acts as the decoder. It is observed that the proposed introduction of the specialized layer is effective in identifying the subset of the most significant features for optimized classification and reconstruction of the data. While training the model, a predefined temperature of the feature selection layer is steadily decreased which allows the model to learn a user specified number of discrete features. In the testing phase, a subset of the features can be selected and used in the decoder to reconstruct the input. }
